Analysis for Revision 2

### 2024-03-12 R/Analysis_v1.2_mash_using_greedy_covar.qmd
manuscript: AH edits from 2024-03-07

```{r}
source("~/Github/Functions_ggplot-theme-adjustments_2018-01-03.R")
mashdir <- here("analysis", "mash_greedy_algorithm", "mash_h2_diag_covar")

@@

@@

cov_gg$ggobject + 
  ggtitle("Gulf greenup", subtitle = "64.5% SNP mass")
cov_gf$ggobject + 
  ggtitle("Gulf flowering", subtitle = "33.0% SNP mass")
cov_mg$ggobject + 
  ggtitle("Midwest greenup", subtitle = "0% SNP mass")
cov_mf$ggobject + 
  ggtitle("Midwest flowering", subtitle = "22.6% SNP mass")
cov_gamg$ggobject + 
  ggtitle("Gulf and Midwest greenup", subtitle = "32.7% SNP mass")
cov_gamf$ggobject + 
  ggtitle("Gulf and Midwest flowering", subtitle = "0% SNP mass")
```

@@

```{r pick covar matrices to plot fig 2}
plot_covar_Ulist_fig2 <- function(df, mf = FALSE, mg = FALSE) {
  if (mg) {
    df <- df %>%
      select(`...1`, TX1, TX2, TX3, OK, MO, NE, MI) 
  } else if (mf) {
    df <- df %>%
      select(`...1`, TX1, TX2, TX3, MO, MI, SD) 
  } else {
    df <- df %>%
      select(`...1`, TX1, TX2, TX3, OK, MO, NE, MI, SD) 
  }

@@

  plot_covar <- U1 %>%
    arrange(desc(rowU), desc(colU)) %>%
    distinct(Site_pair, .keep_all = TRUE) %>%
    ggplot(aes(x = .data$rowU, y = .data$colU)) +
    switchgrassGWAS::theme_oeco +
    geom_tile(aes(fill = .data$covar), na.rm = TRUE) +
    scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                  "white", "#27AD81FF", "#5DC863FF",
                                  "#FDE725FF"),
                         limits = c(-1, 1)) +
    theme(legend.position = "none",
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.line.x = element_blank(),
          axis.line.y = element_blank(),
          axis.title.y.right = element_text()) +
    labs(x = "", y = "")
  return(plot_covar)
}
```

@@

f2b <- df_2gr_b %>%
  filter(Mass > 1e-05) %>%
  ggplot(aes(x = subpop, y = Mass)) + 
  geom_bar(aes(fill = Type), stat = "identity") +
  scale_fill_viridis_d(end = 0.9) +
  theme(axis.title.x=element_blank(),
        legend.position = "none",
        axis.text.x=element_text(hjust = 1, vjust = 1, angle = 45))
f2d <- df_2fl_b %>%
  filter(Mass > 1e-05) %>%
  ggplot(aes(x = subpop, y = Mass)) + 
  geom_bar(aes(fill = Type), stat = "identity") +
  scale_fill_viridis_d(end = 0.9) +
  theme(axis.title.x=element_blank(),
        legend.position = "none",
        axis.text.x=element_text(hjust = 1, vjust = 1, angle = 45))
f2a <- df_2gr_a %>%
  filter(Mass > 1e-06) %>%
  ggplot(aes(x = `Covariance Matrix`, y = Mass)) + 
  geom_bar(aes(fill = Type), stat = "identity") +
  facet_wrap(~subpop) +
  coord_flip() + scale_fill_viridis_d(end = 0.9) +
  theme(legend.position = c(-0.4, 0.3),
        axis.text.x=element_text(hjust = 1, vjust = 1, angle = 45), 
        panel.spacing.x = unit(-0, 'cm')) #+ labs(x = "")
f2c <- df_2fl_a %>%
  filter(Mass > 1e-06) %>%
  ggplot(aes(x = `Covariance Matrix`, y = Mass)) + 
  geom_bar(aes(fill = Type), stat = "identity") +
  facet_wrap(~subpop) +
  coord_flip() + scale_fill_viridis_d(end = 0.9) +
  theme(legend.position = "none",
        axis.text.x=element_text(hjust = 1, vjust = 1, angle = 45), 
        panel.spacing.x = unit(-0, 'cm')) #+ labs(x = "")

@@

ggdraw() +
  draw_plot(pa01, x = -0.02, y = 0.4, width = 0.1, height = 0.18) +
  draw_plot(pa02, x = -0.02, y = 0.6, width = 0.1, height = 0.18) +
  #draw_plot(pa03, x = -0.02, y = 0.6, width = 0.1, height = 0.18) +
  #draw_plot(pa04, x = 0.1, y = 0.6, width = 0.1, height = 0.18) +
  draw_plot(pa05, x = -0.02, y = 0.8, width = 0.1, height = 0.18) +
  draw_plot(pa06, x = -0.02, y = 0, width = 0.1, height = 0.18) +
  draw_plot(pa07, x = -0.02, y = 0.2, width = 0.1, height = 0.18) +
  #draw_plot(pa08, x = 0.2, y = 0, width = 0.1, height = 0.18) +
  draw_plot(pa09, x = 0.13, y = 0.6, width = 0.1, height = 0.18) +
  draw_plot(pa10, x = 0.13, y = 0.2, width = 0.1, height = 0.18) +
  draw_plot(pa11, x = 0.13, y = 0.4, width = 0.1, height = 0.18) +
  draw_plot(pa12, x = 0.13, y = 0, width = 0.1, height = 0.18) +
  draw_plot(pa13, x = 0.13, y = 0.8, width = 0.1, height = 0.18) +
  draw_plot(f2a, x = 0.3, y = 0.47, width = 0.55, height = 0.53) +
  #draw_plot(legend, x = 0.15, y = 0.34, width = 0.1, height = 0.2) +
  draw_plot(f2b, x = 0.85, y = 0.47, width = 0.15, height = 0.53) +
  draw_plot(f2c, x = 0.3, y = 0, width = 0.55, height = 0.47) +
  draw_plot(f2d, x = 0.85, y = 0, width = 0.15, height = 0.47)

@@

save_plot(filename = "../manuscript/Coauthors/PNAS/Revision/Figure_2_Covariance_matrices_and_posterior_weights.svg", plot = last_plot(), base_height = 6, base_width = 8.5)
```

@@

```{r}
sites <- readRDS("~/Github/pvdiv-phenology-gxe/data/sites.rds")

@@

```{r}
get_gxe_summary(gxe_gg) 
get_gxe_summary(gxe_mg, n_cond = 7) 
get_gxe_summary(gxe_gamg, n_sep = 4) 
print("flowering")
get_gxe_summary(gxe_gf) 
get_gxe_summary(gxe_mf, n_cond = 6) 
get_gxe_summary(gxe_gamf, n_sep = 4) 
```

@@

  U1 <- as_tibble(U1, rownames = "rowU", .name_repair = "unique") %>%
          pivot_longer(cols = -.data$rowU, names_to = "colU",
                       values_to = "covar") %>%
          filter(!is.na(.data$covar)) %>%
    mutate(rowU = str_remove(rowU, 
                             "Stand_BhatGulf_and_Midwest_")) %>%
    mutate(rowU = str_remove(rowU, "Stand_BhatGulf_")) %>%
    mutate(rowU = str_remove(rowU, "Stand_BhatMidwest_")) %>%
    mutate(rowU = str_remove(rowU, "GR50_")) %>%
    mutate(rowU = str_remove(rowU, "FL50_")) %>%
    mutate(colU = str_remove(colU, 
                             "Stand_BhatGulf_and_Midwest_")) %>%
    mutate(colU = str_remove(colU, "Stand_BhatGulf_")) %>%
    mutate(colU = str_remove(colU, "Stand_BhatMidwest_")) %>%
    mutate(colU = str_remove(colU, "GR50_")) %>%
    mutate(colU = str_remove(colU, "FL50_")) %>%
    mutate(rowU = case_when(grepl("^M$", rowU) ~ "MI",
                            TRUE ~ rowU),
           colU = case_when(grepl("^M$", colU) ~ "MI",
                            TRUE ~ colU),)
  U1$colU <- factor(U1$colU, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"))
  U1$rowU <- factor(U1$rowU, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"))
  U1 <- arrange(U1, rowU, colU) %>%
    pivot_wider(names_from = colU, values_from = covar) 
  for(i in 1:nrow(U1)){
    for(j in 2:ncol(U1)){
      if(i <= j-1){
        U1[i, j] <- NA
      }
    }
  }
  U1 <- U1 %>%
    pivot_longer(cols = -.data$rowU, names_to = "colU",
                       values_to = "covar")
  U1$colU <- factor(U1$colU, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD")) 
  if(is.null(upper)){
  upper <- max(U1$covar, na.rm = TRUE)+5
  }
  U1_covar <- U1 %>%
    filter(!is.na(.data$covar)) %>%
    ggplot(aes(x = .data$rowU, y = .data$colU)) +
    switchgrassGWAS::theme_oeco +
    geom_tile(aes(fill = .data$covar)) +
    scale_fill_viridis_c(option = "B", limits = c(0, upper)) +
    #geom_text(aes(label = round(.data$covar, 1)), color = "darkgrey") +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    xlab("") + ylab("") 
  if(legend == TRUE){
    U1_covar <- U1_covar +
      theme(legend.position = c(0.2, 0.9)) +
      geom_text(aes(label = round(.data$covar, 1)), color = "darkgrey")
  }
  return(U1_covar)
}

@@

```{r}
 pvdiv_plot_cor(corrmatrix = gxe_gamf$S_AP, legend = TRUE) + 
  labs(subtitle = " ")
```

```{r}
p3legend <- pvdiv_plot_cor(corrmatrix = gxe_gg$S_AP, legend = TRUE, upper = 4333) + 
  labs(title = "Gulf", subtitle = "Sign difference")
legend <- get_legend(p3legend)

p3a1 <- pvdiv_plot_cor(corrmatrix = gxe_gg$S_AP, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3a2 <- pvdiv_plot_cor(corrmatrix = gxe_gg$S_DS, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3a3 <- pvdiv_plot_cor(corrmatrix = gxe_gg$S_2_no, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3b1 <- pvdiv_plot_cor(corrmatrix = gxe_mg$S_AP, legend = FALSE, upper = 4333) + 
  labs(subtitle = "Sign difference")
p3b2 <- pvdiv_plot_cor(corrmatrix = gxe_mg$S_DS, legend = FALSE, upper = 4333) + 
  labs(subtitle = "Magnitude difference")
p3b3 <- pvdiv_plot_cor(corrmatrix = gxe_mg$S_2_no, legend = FALSE, upper = 4333) + 
  labs(subtitle = "Not distinguishable")
p3c1 <- pvdiv_plot_cor(corrmatrix = gxe_gamg$S_AP, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3c2 <- pvdiv_plot_cor(corrmatrix = gxe_gamg$S_DS, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3c3 <- pvdiv_plot_cor(corrmatrix = gxe_gamg$S_2_no, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")

p3d1 <- pvdiv_plot_cor(corrmatrix = gxe_gf$S_AP, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3d2 <- pvdiv_plot_cor(corrmatrix = gxe_gf$S_DS, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3d3 <- pvdiv_plot_cor(corrmatrix = gxe_gf$S_2_no, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3e1 <- pvdiv_plot_cor(corrmatrix = gxe_mf$S_AP, legend = FALSE, upper = 4333) + 
  labs(subtitle = "Sign difference")
p3e2 <- pvdiv_plot_cor(corrmatrix = gxe_mf$S_DS, legend = FALSE, upper = 4333) + 
  labs(subtitle = "Magnitude difference")
p3e3 <- pvdiv_plot_cor(corrmatrix = gxe_mf$S_2_no, legend = FALSE, upper = 4333) + 
  labs(subtitle = "Not distinguishable")
p3f1 <- pvdiv_plot_cor(corrmatrix = gxe_gamf$S_AP, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3f2 <- pvdiv_plot_cor(corrmatrix = gxe_gamf$S_DS, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
p3f3 <- pvdiv_plot_cor(corrmatrix = gxe_gamf$S_2_no, legend = FALSE, upper = 4333) + 
  labs(subtitle = " ")
```

```{r build figure 3}
ggdraw() +
  draw_plot(p3a1, x = 0, y = .82, width = 1/3, height = .18) +
  draw_plot(p3a2, x = 0, y = 4/6, width = 1/3, height = .18) +
  draw_plot(p3a3, x = 0, y = .51, width = 1/3, height = .18) +
  draw_plot(p3b1, x = 0.33, y = .82, width = 1/3, height = .18) +
  draw_plot(p3b2, x = 0.33, y = 4/6, width = 1/3, height = .18) +
  draw_plot(p3b3, x = 0.33, y = .51, width = 1/3, height = .18) +
  draw_plot(p3c1, x = 0.66, y = .82, width = 1/3, height = .18) +
  draw_plot(p3c2, x = 0.66, y = 4/6, width = 1/3, height = .18) +
  draw_plot(p3c3, x = 0.66, y = .51, width = 1/3, height = .18) +
  draw_plot(p3d1, x = 0, y = 2/6, width = 1/3, height = .18) +
  draw_plot(p3d2, x = 0, y = 1/6, width = 1/3, height = .18) +
  draw_plot(p3d3, x = 0, y = 0/6, width = 1/3, height = .18) +
  draw_plot(p3e1, x = 0.33, y = 2/6, width = 1/3, height = .18) +
  draw_plot(p3e2, x = 0.33, y = 1/6, width = 1/3, height = .18) +
  draw_plot(p3e3, x = 0.33, y = 0/6, width = 1/3, height = .18) +
  draw_plot(p3f1, x = 0.66, y = 2/6, width = 1/3, height = .18) +
  draw_plot(p3f2, x = 0.66, y = 1/6, width = 1/3, height = .18) +
  draw_plot(p3f3, x = 0.66, y = 0/6, width = 1/3, height = .18) +
  draw_plot(legend, x = 0.37, y = .38, width = 1/3, height = .18)

>>>>

```{r}
mashdir <- here("analysis", "mash_greedy_algorithm", "mash_h2_diag_covar")

@@

New theme for ggplot2 v 3.5

```{r}
theme_oeco <- theme_classic() +
  theme(axis.title = element_text(size = 10), 
        axis.text = element_text(size = 10), 
        axis.line.x = element_line(linewidth = 0.35, colour = 'grey50'),
        axis.line.y = element_line(linewidth = 0.35, colour = 'grey50'),
        axis.ticks = element_line(linewidth = 0.25, colour = 'grey50'), 
        legend.justification = c(1, 0.75), 
        legend.position = c(1, 0.9), 
        legend.key.size = unit(0.35, 'cm'),
        legend.title = element_blank(), 
        legend.text = element_text(size = 9),
        legend.background = element_blank(),
        plot.subtitle = element_text(size = 10, vjust = 0), #plot.margin = unit(c(0.35, 0, 0.25, 0), 'cm'),
        strip.background = element_blank(), 
        strip.text = element_text(hjust = 0.5, size = 10 ,vjust = 0), 
        strip.placement = 'outside', panel.spacing.x = unit(-0.5, 'cm'))
theme_set(theme_oeco)
```

@@

cov_gg$ggobject + 
  theme_oeco +
  ggtitle("Gulf greenup", subtitle = "64.5% SNP mass")
cov_gf$ggobject + 
  theme_oeco +
  ggtitle("Gulf flowering", subtitle = "33.0% SNP mass")
cov_mg$ggobject + 
  theme_oeco +
  ggtitle("Midwest greenup", subtitle = "0% SNP mass")
cov_mf$ggobject + 
  theme_oeco +
  ggtitle("Midwest flowering", subtitle = "22.6% SNP mass")
cov_gamg$ggobject + 
  theme_oeco +
  ggtitle("Gulf and Midwest greenup", subtitle = "32.7% SNP mass")
cov_gamf$ggobject + 
  theme_oeco +
  ggtitle("Gulf and Midwest flowering", subtitle = "0% SNP mass")
```

@@

```{r pick covar matrices to plot fig 2}
plot_covar_Ulist_fig2 <- function(df, mf = FALSE, mg = FALSE, legend = FALSE) {
  if (mg) {
    df <- df %>%
      select(`...1`, TX1, TX2, TX3, OK, MO, NE, MI) 
  } else if (mf) {
    df <- df %>%
      select(`...1`, TX1, TX2, TX3, MO, MI, SD) 
  } else {
    df <- df %>%
      select(`...1`, TX1, TX2, TX3, OK, MO, NE, MI, SD) 
  }

@@

  plot_covar <- U1 %>%
    arrange(desc(rowU), desc(colU)) %>%
    distinct(Site_pair, .keep_all = TRUE) %>%
    ggplot(aes(x = .data$rowU, y = .data$colU)) +
    switchgrassGWAS::theme_oeco +
    geom_tile(aes(fill = .data$covar), na.rm = TRUE) +
    scale_fill_gradientn(colors = c("#30123BFF", "#4777EFFF", "#1BD0D5FF",
                                  "white", "#FE9B2DFF", "#DB3A07FF",
                                  "#7A0403FF"),
                         limits = c(-1, 1)) +
    theme_oeco 
  if (legend == FALSE) {
    plot_covar <- plot_covar +
    theme(legend.position = "none",
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.line.x = element_blank(),
          axis.line.y = element_blank(),
          axis.title.y.right = element_text()) +
    labs(x = "", y = "")
  } else if (legend == TRUE) {
      plot_covar <- plot_covar +
    theme(legend.position = "right",
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.line.x = element_blank(),
          axis.line.y = element_blank(),
          axis.title.y.right = element_text()) +
    labs(x = "", y = "")
    }

  return(plot_covar)
}
library(scales)
show_col(viridis_pal(option = "H")(8))
```

@@

f2b <- df_2gr_b %>%
  filter(Mass > 1e-05) %>%
  ggplot(aes(x = subpop, y = Mass)) + 
  geom_bar(aes(fill = Type), stat = "identity") +
  scale_fill_viridis_d(end = 0.9, option = "H") +
  theme_oeco + 
  theme(axis.title.x=element_blank(),
        legend.position = "none",
        axis.text.x=element_text(hjust = 1, vjust = 1, angle = 45))
f2d <- df_2fl_b %>%
  filter(Mass > 1e-05) %>%
  ggplot(aes(x = subpop, y = Mass)) + 
  geom_bar(aes(fill = Type), stat = "identity") +
  scale_fill_viridis_d(end = 0.9, option = "H") +
  theme_oeco + 
  theme(axis.title.x=element_blank(),
        legend.position = "none",
        axis.text.x=element_text(hjust = 1, vjust = 1, angle = 45))
f2a <- df_2gr_a %>%
  filter(Mass > 1e-06) %>%
  ggplot(aes(x = `Covariance Matrix`, y = Mass)) + 
  geom_bar(aes(fill = Type), stat = "identity") +
  facet_wrap(~subpop) +
  coord_flip() + scale_fill_viridis_d(end = 0.9, option = "H") +
  theme(legend.position = c(-0.4, 0.3),
        axis.text.x=element_text(hjust = 1, vjust = 1, angle = 45), 
        panel.spacing.x = unit(-0, 'cm')) #+ labs(x = "")
f2c <- df_2fl_a %>%
  filter(Mass > 1e-06) %>%
  ggplot(aes(x = `Covariance Matrix`, y = Mass)) + 
  geom_bar(aes(fill = Type), stat = "identity") +
  facet_wrap(~subpop) +
  coord_flip() + scale_fill_viridis_d(end = 0.9, option = "H") +
  theme(legend.position = "none",
        axis.text.x=element_text(hjust = 1, vjust = 1, angle = 45), 
        panel.spacing.x = unit(-0, 'cm')) #+ labs(x = "")

pa_legend <- plot_covar_Ulist_fig2(Ulist_gg$`Daylength (14d prior)`, legend = TRUE) + 
  labs(subtitle = "Daylength (14d prior)")
legend <- get_legend(pa_legend) 
```

@@

ggdraw() +
  theme_oeco + 
  draw_plot(pa01, x = -0.02, y = 0.4, width = 0.1, height = 0.18) +
  draw_plot(pa02, x = -0.02, y = 0.6, width = 0.1, height = 0.18) +
  #draw_plot(pa03, x = -0.02, y = 0.6, width = 0.1, height = 0.18) +
  #draw_plot(pa04, x = 0.1, y = 0.6, width = 0.1, height = 0.18) +
  draw_plot(pa05, x = -0.02, y = 0.8, width = 0.1, height = 0.18) +
  draw_plot(pa06, x = -0.02, y = 0, width = 0.1, height = 0.18) +
  draw_plot(pa07, x = -0.02, y = 0.2, width = 0.1, height = 0.18) +
  #draw_plot(pa08, x = 0.2, y = 0, width = 0.1, height = 0.18) +
  draw_plot(pa09, x = 0.13, y = 0.6, width = 0.1, height = 0.18) +
  draw_plot(pa10, x = 0.13, y = 0.2, width = 0.1, height = 0.18) +
  draw_plot(pa11, x = 0.13, y = 0.4, width = 0.1, height = 0.18) +
  draw_plot(pa12, x = 0.13, y = 0, width = 0.1, height = 0.18) +
  draw_plot(pa13, x = 0.13, y = 0.8, width = 0.1, height = 0.18) +
  draw_plot(f2a, x = 0.3, y = 0.47, width = 0.55, height = 0.53) +
  draw_plot(legend, x = 0.15, y = 0.34, width = 0.1, height = 0.2) +
  draw_plot(f2b, x = 0.85, y = 0.47, width = 0.15, height = 0.53) +
  draw_plot(f2c, x = 0.3, y = 0, width = 0.55, height = 0.47) +
  draw_plot(f2d, x = 0.85, y = 0, width = 0.15, height = 0.47)

@@

save_plot(filename = "../manuscript/revision2/Figure_2_recolor_covariance_matrices_and_posterior_weights.svg", plot = last_plot(), base_height = 5.5, base_width = 8)
```

@@

```{r}
sites <- readRDS(here("data/sites.rds"))

@@

```{r}
fig3_gg <- get_gxe_summary(gxe_gg) 
fig3_mg <- get_gxe_summary(gxe_mg, n_cond = 7) 
fig3_bg <- get_gxe_summary(gxe_gamg, n_sep = 4) 
print("flowering")
fig3_gf <- get_gxe_summary(gxe_gf) 
fig3_mf <- get_gxe_summary(gxe_mf, n_cond = 6) 
fig3_bf <- get_gxe_summary(gxe_gamf, n_sep = 4) 
```

```{r}
fig3_fractions <- fig3_gg$gxe_fractions |> 
  mutate(Phenotype = "Greenup Date",
         Population = "Gulf") |> 
  full_join(fig3_mg$gxe_fractions) |> 
  mutate(Phenotype = case_when(is.na(Phenotype) ~ "Greenup Date",
                               TRUE ~ Phenotype),
         Population = case_when(is.na(Population) ~ "Midwest",
                               TRUE ~ Population),
         ) |> 
  full_join(fig3_bg$gxe_fractions) |> 
  mutate(Phenotype = case_when(is.na(Phenotype) ~ "Greenup Date",
                               TRUE ~ Phenotype),
         Population = case_when(is.na(Population) ~ "Both",
                               TRUE ~ Population),
         ) |> 
  full_join(fig3_gf$gxe_fractions) |> 
  mutate(Phenotype = case_when(is.na(Phenotype) ~ "Flowering Date",
                               TRUE ~ Phenotype),
         Population = case_when(is.na(Population) ~ "Gulf",
                               TRUE ~ Population),
         ) |> 
  full_join(fig3_mf$gxe_fractions) |> 
  mutate(Phenotype = case_when(is.na(Phenotype) ~ "Flowering Date",
                               TRUE ~ Phenotype),
         Population = case_when(is.na(Population) ~ "Midwest",
                               TRUE ~ Population),
         ) |> 
  full_join(fig3_bf$gxe_fractions) |> 
  mutate(Phenotype = case_when(is.na(Phenotype) ~ "Flowering Date",
                               TRUE ~ Phenotype),
         Population = case_when(is.na(Population) ~ "Both",
                               TRUE ~ Population),
         )
```

```{r}
fig3_fractions <- fig3_fractions |> 
  rename(`North vs North` = North_North,
         `North vs Texas` = North_Texas,
         `Texas vs Texas` = Texas_Texas) |> 
  pivot_longer(cols = `North vs North`:`Texas vs Texas`, names_to = "Regions", values_to = "Fraction of Effects with this GxE Type")

fig3_fractions$Type_of_GxE <- factor(fig3_fractions$Type_of_GxE, levels = c("Sign", "Magnitude", "None"))
fig3_fractions$Phenotype <- factor(fig3_fractions$Phenotype, 
                                   levels = c("Greenup Date", "Flowering Date"))
fig3_fractions$Population <- factor(fig3_fractions$Population, 
                                     levels = c("Gulf", "Midwest", "Both"))
fig3_frac_plot <- fig3_fractions |> 
  ggplot(aes(x = Regions, y = `Fraction of Effects with this GxE Type`)) + 
  geom_bar(aes(fill = Type_of_GxE), position = "stack", stat = "identity", color = "black") + 
  facet_grid(Phenotype ~ Population) +
  scale_fill_manual(values = c("#440154FF", "#5DC863FF",
                                  "white")) +
  theme(legend.position = "top",
        panel.spacing.x = unit(0.1, "mm"), 
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

ggdraw() +
  theme_oeco +
  draw_plot(fig3_frac_plot, x = 0, y = 0, width = 1, height = .67)
save_plot(filename = "../manuscript/revision2/Figure_3_Fraction_GxE_by_Region.svg", base_height = 6, base_width = 4.5, plot = last_plot())
```

```{r}
p1 <- mash_plot_effects(m_gulf_gr_hyp, n = 1)
p1$ggobject + 
  theme_oeco + 
  coord_flip()

save_plot(filename = "../manuscript/revision2/Figure_3_GxE_Types_Example.svg", base_height = 3, base_width = 2.5, plot = last_plot())
```

@@

  U1 <- as_tibble(U1, rownames = "rowU", .name_repair = "unique") %>%
          pivot_longer(cols = -.data$rowU, names_to = "colU",
                       values_to = "covar") %>%
          filter(!is.na(.data$covar)) %>%
    mutate(rowU = str_remove(rowU, 
                             "Stand_BhatGulf_and_Midwest_")) %>%
    mutate(rowU = str_remove(rowU, "Stand_BhatGulf_")) %>%
    mutate(rowU = str_remove(rowU, "Stand_BhatMidwest_")) %>%
    mutate(rowU = str_remove(rowU, "GR50_")) %>%
    mutate(rowU = str_remove(rowU, "FL50_")) %>%
    mutate(colU = str_remove(colU, 
                             "Stand_BhatGulf_and_Midwest_")) %>%
    mutate(colU = str_remove(colU, "Stand_BhatGulf_")) %>%
    mutate(colU = str_remove(colU, "Stand_BhatMidwest_")) %>%
    mutate(colU = str_remove(colU, "GR50_")) %>%
    mutate(colU = str_remove(colU, "FL50_")) %>%
    mutate(rowU = case_when(grepl("^M$", rowU) ~ "MI",
                            TRUE ~ rowU),
           colU = case_when(grepl("^M$", colU) ~ "MI",
                            TRUE ~ colU),)
  U1$colU <- factor(U1$colU, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"))
  U1$rowU <- factor(U1$rowU, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"))
  U1 <- arrange(U1, rowU, colU) %>%
    pivot_wider(names_from = colU, values_from = covar) 
  for(i in 1:nrow(U1)){
    for(j in 2:ncol(U1)){
      if(i <= j-1){
        U1[i, j] <- NA
      }
    }
  }
  U1 <- U1 %>%
    pivot_longer(cols = -.data$rowU, names_to = "colU",
                       values_to = "covar")
  U1$colU <- factor(U1$colU, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD")) 
  if(is.null(upper)){
  upper <- max(U1$covar, na.rm = TRUE)+5
  }
  U1_covar <- U1 %>%
    filter(!is.na(.data$covar)) %>%
    ggplot(aes(x = .data$rowU, y = .data$colU)) +
    switchgrassGWAS::theme_oeco +
    geom_tile(aes(fill = .data$covar)) +
    scale_fill_viridis_c(option = "H", limits = c(0, upper)) +
    #geom_text(aes(label = round(.data$covar, 1)), color = "darkgrey") +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    xlab("") + ylab("") 
  if(legend == TRUE){
    U1_covar <- U1_covar +
      theme(legend.position = c(0.2, 0.9)) +
      geom_text(aes(label = round(.data$covar, 1)), color = "darkgrey")
  }
  return(U1_covar)
}

@@

```{r}
 pvdiv_plot_cor(corrmatrix = gxe_gamf$S_AP, legend = TRUE) + 
  theme_oeco +
  labs(subtitle = " ")
```

```{r}
p3legend <- pvdiv_plot_cor(corrmatrix = gxe_gg$S_AP, legend = TRUE, 
                           upper = 4333) + 
  theme_oeco +
  labs(title = "Gulf", subtitle = "Sign difference")
legend <- get_legend(p3legend)

p3a1 <- pvdiv_plot_cor(corrmatrix = gxe_gg$S_AP, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3a2 <- pvdiv_plot_cor(corrmatrix = gxe_gg$S_DS, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3a3 <- pvdiv_plot_cor(corrmatrix = gxe_gg$S_2_no, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3b1 <- pvdiv_plot_cor(corrmatrix = gxe_mg$S_AP, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = "Sign difference")
p3b2 <- pvdiv_plot_cor(corrmatrix = gxe_mg$S_DS, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = "Magnitude difference")
p3b3 <- pvdiv_plot_cor(corrmatrix = gxe_mg$S_2_no, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = "Not distinguishable")
p3c1 <- pvdiv_plot_cor(corrmatrix = gxe_gamg$S_AP, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3c2 <- pvdiv_plot_cor(corrmatrix = gxe_gamg$S_DS, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3c3 <- pvdiv_plot_cor(corrmatrix = gxe_gamg$S_2_no, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")

p3d1 <- pvdiv_plot_cor(corrmatrix = gxe_gf$S_AP, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3d2 <- pvdiv_plot_cor(corrmatrix = gxe_gf$S_DS, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3d3 <- pvdiv_plot_cor(corrmatrix = gxe_gf$S_2_no, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3e1 <- pvdiv_plot_cor(corrmatrix = gxe_mf$S_AP, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = "Sign difference")
p3e2 <- pvdiv_plot_cor(corrmatrix = gxe_mf$S_DS, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = "Magnitude difference")
p3e3 <- pvdiv_plot_cor(corrmatrix = gxe_mf$S_2_no, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = "Not distinguishable")
p3f1 <- pvdiv_plot_cor(corrmatrix = gxe_gamf$S_AP, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3f2 <- pvdiv_plot_cor(corrmatrix = gxe_gamf$S_DS, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
p3f3 <- pvdiv_plot_cor(corrmatrix = gxe_gamf$S_2_no, legend = FALSE, 
                       upper = 4333) + 
  theme_oeco +
  labs(subtitle = " ")
```

```{r build figure 3}
ggdraw() +
  theme_oeco +
  draw_plot(p3a1, x = 0, y = .82, width = 1/3, height = .18) +
  draw_plot(p3a2, x = 0, y = 4/6, width = 1/3, height = .18) +
  draw_plot(p3a3, x = 0, y = .51, width = 1/3, height = .18) +
  draw_plot(p3b1, x = 0.33, y = .82, width = 1/3, height = .18) +
  draw_plot(p3b2, x = 0.33, y = 4/6, width = 1/3, height = .18) +
  draw_plot(p3b3, x = 0.33, y = .51, width = 1/3, height = .18) +
  draw_plot(p3c1, x = 0.66, y = .82, width = 1/3, height = .18) +
  draw_plot(p3c2, x = 0.66, y = 4/6, width = 1/3, height = .18) +
  draw_plot(p3c3, x = 0.66, y = .51, width = 1/3, height = .18) +
  draw_plot(p3d1, x = 0, y = 2/6, width = 1/3, height = .18) +
  draw_plot(p3d2, x = 0, y = 1/6, width = 1/3, height = .18) +
  draw_plot(p3d3, x = 0, y = 0/6, width = 1/3, height = .18) +
  draw_plot(p3e1, x = 0.33, y = 2/6, width = 1/3, height = .18) +
  draw_plot(p3e2, x = 0.33, y = 1/6, width = 1/3, height = .18) +
  draw_plot(p3e3, x = 0.33, y = 0/6, width = 1/3, height = .18) +
  draw_plot(p3f1, x = 0.66, y = 2/6, width = 1/3, height = .18) +
  draw_plot(p3f2, x = 0.66, y = 1/6, width = 1/3, height = .18) +
  draw_plot(p3f3, x = 0.66, y = 0/6, width = 1/3, height = .18) +
  draw_plot(legend, x = 0.37, y = .38, width = 1/3, height = .18)
